---
title       : Prince Song Recommender
subtitle    : Building a song recommender using the Million Song Dataset
author      : Telvis Calhoun
job         : Research Engineer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      #
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Goals

- Create a song recommender using metadata from the [Million Song Dataset](http://labrosa.ee.columbia.edu/millionsong/).  
- Create a demo recommender application using [R and Shiny](http://shiny.rstudio.com/)
- Recommend songs by [US recording artist 'Prince'](https://en.wikipedia.org/wiki/Prince_(musician) )

--- .class #id

## Getting and Cleaning the Data

- The entire dataset is 280GB and Stored in Amazon S3 in [HDF5](https://www.hdfgroup.org/HDF5/) format.
- We ran a data extraction script on EC2 to a serialized R file containing the features.

```{r, echo=TRUE, cache=TRUE}
df <- readRDS("data/songs.rds")
names(df)
```

--- .class #id

## Feature Selection

Song Hotttnesss : Measures the popularity of the song.

```{r, echo=FALSE,message=FALSE}
# First, lets load libraries and datasets used in the analysis.
library(ggplot2)
```

```{r echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
qplot(song_hotttnesss, data=df)
```

***

Loudness : Measures the audio volume of the song.

```{r echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
qplot(loudness, data=df)
```
